
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1.0 cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, nosep}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}

\begin{center}
{\LARGE \textbf{Madhu Kandukuri}}\\[6pt]
Hyderabad, Telangana, India \textbar\ 
\href{mailto:madhu.kandukuri419@gmail.com}{madhu.kandukuri419@gmail.com} \textbar\ 
+91 9573673706 \textbar\ 
\href{https://www.linkedin.com/in/madhu-kandukuri-ab97341b9/}{linkedin.com/in/madhu-kandukuri-ab97341b9}
\end{center}

\section*{Summary}

Salesforce Administrator with 3.3 years of experience managing enterprise Salesforce environments across Sales Cloud and Service Cloud. Expertise in system configuration, security architecture, automation using Record-Triggered Flows, Agentforce AI enablement, and DevOps-driven deployments using Copado and CI/CD pipelines. Proven track record of supporting 500+ users, delivering zero-defect production releases, and improving service efficiency through intelligent automation and governed release management.

\section*{Work Experience}

\textbf{Salesforce Administrator} \hfill Dec 2022 -- Present\\
Accenture, Hyderabad, India

\textbf{Project: Enterprise Sales \& Case Management System}

\begin{itemize}

\item Administered Salesforce org supporting 500+ users across Sales and Service operations.

\item Designed and implemented \textbf{Record-Triggered Flows} and Approval Processes to automate case routing and escalations, reducing manual effort by 40\%.

\item Configured \textbf{Roles, Profiles, Permission Sets, OWD, Sharing Rules, and Field-Level Security} ensuring secure and compliant data access.

\item Built executive-level \textbf{Reports and Dashboards} improving operational visibility and decision-making efficiency.

\item Implemented \textbf{Agentforce AI capabilities} including intelligent case summarization, dynamic routing, and response suggestions, reducing average handling time and improving agent productivity.

\item Configured Email-to-Case routing addresses, auto-response rules, and case assignment rules; implemented Omni-Channel with queue-based routing, agent presence statuses, and capacity models to streamline case distribution.

\item Executed end-to-end deployments (Dev → QA → UAT → Production) using \textbf{Copado, Change Sets, and Salesforce DX (SFDX)} ensuring controlled, auditable, and rollback-ready releases.

\item Conducted post-deployment validation, smoke testing, and maintained zero rollback incidents during quarterly production releases.

\item Managed Record Types and Page Layouts across Case and Account objects to enforce role-appropriate data entry; conducted root-cause analysis on configuration issues and documented solutions to reduce repeat tickets.



\item Provided L1 and L2 level Salesforce support, troubleshooting configuration issues, performing root-cause analysis, and maintaining a knowledge base of documented resolutions to ensure smooth business operations and SLA compliance.

\end{itemize}

\section*{Technical Skills}

\textbf{Salesforce Technologies:} Flows (Record-Triggered, Scheduled), Validation Rules, Approval Processes, Reports, Dashboards, Roles, Profiles, Permission Sets, Sharing Rules, OWD, Field-Level Security, Email-to-Case, Omni-Channel routing, Sales Cloud, Service Cloud, Entitlements, Dynamic Forms, Service Console

\textbf{AI \& Automation:} Agentforce, Agentforce Prompt Templates, AI-driven Case Routing, Case Summarization

\textbf{Deployment \& DevOps:} Copado DevOps, Change Sets, Salesforce DX (SFDX), Git, GitHub, Azure DevOps, CI/CD Pipelines, Sandbox Management

\textbf{Data Management:} Data Loader, Data Import Wizard, Bulk Data Handling, Duplicate Management

\textbf{Tools:} Salesforce Workbench, VS Code, Jira, Salesforce Inspector

\section*{Education}

\textbf{B.Tech -- Electronics and Communication Engineering} \hfill 2022\\
Gokaraju Rangaraju Institute of Engineering and Technology, Hyderabad \hfill CGPA: 8.4

\section*{Certifications}

\begin{itemize}
\item Salesforce Certified Administrator
\item Salesforce Platform Developer I
\item Salesforce Agentforce Specialist
\end{itemize}

\end{document}